### 2021-04-08 priority-cp.tex
a quick pass to the paper

\noindent
\textbf{Milner's Cyclic Scheduler}.
As an example of a deadlock-free cyclic process, Dardha and Gay~\cite{dardhagay18} introduce an implementation of Milner's cyclic scheduler~\cite{milner89} in Priority CP. We have reproduced the scheduler in our updated PCP, and showed its translation to PGV. Full details are given in \cref{sec:milner}.

>>>>

%\noindent
%\textbf{Milner's Cyclic Scheduler}.
%As an example of a deadlock-free cyclic process, Dardha and Gay~\cite{dardhagay18} introduce an implementation of Milner's cyclic scheduler~\cite{milner89} in Priority CP. We have reproduced the scheduler in our updated PCP, and showed its translation to PGV. Full details are given in \cref{sec:milner}.
